Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-05-27 publication_materials/ms_rbc.tex
appendix D completed

\section{Timestep Management} \label{sec:timestep}
To find MSTE, we advance $\overline{T}$ by timesteps of size $\Delta t$.
For large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
This is due to coupling between the eigenfunctions $W(z)$, $\Theta(z)$ and the mean temperature profile $\overline{T}$.
In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
This is not a numerical instability, rather, it is an inherent limitation of our timestepping algorithm.
To curtail this, we halt the root-finding algorithms after 20 successive approximations, and reduce the timestep by a factor of 1.1, and try again.

@@

\onecolumngrid
\section{MSTE Properties, Parameters, and Results}\label{sec:tables}

@@

% \section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
\begin{figure}
    \centering
    \includegraphics[width=7.1in]{grid_vars.pdf}
    \caption{The real and imaginary components of the temperature and pressure MSTE eigenfunctions are illustrated in separate plots for various marginally-stable modes. 
    For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
    In both other cases ($k_x = 5.5\pi, \, 17.5\pi$) the vertical velocity is localized near the boundaries.
    In the temperature eigenfunction $\Theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.}%
    \label{fig:eigenfunctions}%
\end{figure}

>>>>

\section{Timestep Management} \label{sec:timestep}
To find MSTE, we advance $\overline{T}$ by timesteps of size $\Delta t$.
For large $\Delta t$, we find the advective flux terms fail to provide a stabilizing influence.
This is due to coupling between the eigenfunctions $W(z)$, $\theta(z)$ and the mean temperature profile $\overline{T}$.
In the context of our algorithm, this effectively deletes the sought-after root of the maximum eigenvalue function $\sigma_{\rm{max}}(A^2)$, causing the root-finding methods to fail. 
This is not a numerical instability, rather, it is an inherent limitation of our timestepping algorithm.
To curtail this, we halt the root-finding algorithms after 20 successive approximations, and reduce the timestep by a factor of 1.1, and try again.

@@

\onecolumngrid
\section{MSTE Parameters, and Results}\label{sec:tables}

@@

\clearpage
\section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
\begin{figure}[H]
    \centering
    \includegraphics[width=7.1in]{grid_vars.pdf}
    \caption{The temperature and pressure MSTE eigenfunctions are shown in separate plots for various marginally-stable modes. 
    Adjacent modes, whose wavenumbers only differ by $\pi/2$, are superimposed to illustrate their similarity.
    For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
    As $k_x$ increases, the vertical velocity is becomes more localized to the boundaries.
    This trend is also apparent in the two pairs of adjacent modes.
    In the temperature eigenfunctions $\theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.
    The left-most peaks of these profiles approximately coincide with the previously-defined boundary layer height $\delta$.
    }%
    \label{fig:eigenfunctions}%
\end{figure}
